---
title: "CoDEx 2024"
author: "Christina Maimone"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

```{r}
library(tidyverse)
library(ggthemes)
library(readxl)
library(ggbeeswarm)
library(ggpubr)
```

```{r}
save_plots <- FALSE
```


# Line Plot

Data is from:
Homan, C. P. (2024). Understanding Competition in Social Space: Religious Congregations in Manhattan, 1949 to 1999. American Sociological Review, 89(1), 60-87. https://doi.org/10.1177/00031224231221561

Data values are approximate, as they were extracted from the plot rather than a data file.  The data is: Percent of Congregations in the Manhattan Yellow Pages with Either Bold Font or a Box Advertisement, 1949 to 1999.

```{r}
congregations <- read_csv("lineplot.csv")
```


## Original

The original visualization was likely created in Stata.  This is an approximation in R

```{r, fig.width=6, fig.height=4}
congregations %>%
  ggplot(aes(x=year, y=percent)) +
  geom_line(col="navyblue", linewidth=.4) + 
  scale_y_continuous(limits=c(0, 10),
                     breaks=seq(0,10,2)) +
  labs(y="Percent", 
       x="Year") +
  theme_stata() +
  theme(text = element_text(family="Times New Roman"),
        axis.text.y = element_text(angle=0),
        line = element_line(linewidth=.3))
```

Here's an equivalent default line plot in R

```{r, fig.width=6, fig.height=4}
congregations %>%
  ggplot(aes(x=year, y=percent)) +
  geom_line() +
  scale_y_continuous(limits=c(0,10)) +
  labs(y="Percent", 
       x="Year") +
  theme_bw()

if (save_plots) ggsave("line_rdefault.png", width=6, height=4)
```


## Revision Options


### Remove the background, change the font

Default to sans-serif fonts, like Arial, Helvetica, or even Calibri

```{r, fig.width=6, fig.height=4}
p1_base <- congregations %>%
  ggplot(aes(x=year, y=percent)) +
  geom_line() +
  scale_y_continuous(limits=c(0,10),
                     breaks=seq(0,10,2)) +
  labs(y="Percent", 
       x="Year") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank())

p1_base

if (save_plots) ggsave(p1_base, filename="line1.png", width=6, height=4)
```



### Labels

```{r, fig.width=6, fig.height=4}
# start with the plot above and make some changes
p1_labels <- p1_base +
  scale_y_continuous(limits=c(0,10),
                     breaks=seq(0,10,2),
                     labels=scales::label_percent(scale = 1)) +
  labs(y="Congregations Advertising",
       x=NULL)

p1_labels
if (save_plots) ggsave(p1_labels, filename="line2.png", width=6, height=4)
```


### Lines

```{r, fig.width=6, fig.height=4}
p1_lines <- congregations %>%
  ggplot(aes(x=year, y=percent)) +
  # thicken the data line a bit
  geom_line(linewidth=0.75) +
  scale_y_continuous(limits=c(0,10),
                     breaks=seq(0,10,2),
                     labels=scales::label_percent(scale = 1),
                     # remove spacing at bottom
                     expand = c(0, NA)) +
  labs(y="Congregations Advertising",
       x=NULL) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        # remove borders
        panel.border = element_blank(),
        # remove tick marks separate from grid
        axis.ticks.y = element_blank())

p1_lines +
  theme(axis.line.y.left = element_line(linewidth=.25),
        axis.line.x.bottom = element_line(linewidth=.25))

if (save_plots) ggsave(filename="line3.png", width=6, height=4)

p1_lines +
  theme(panel.grid.major.y = element_line(color="gray80"))

if (save_plots) ggsave(filename="line4.png", width=6, height=4)

p1_lines +
  scale_y_continuous(limits=c(0,10),
                     breaks=seq(0,9,3),
                     labels=scales::label_percent(scale = 1),
                     expand = c(0, NA)) +
  theme(panel.grid.major.y = element_line(color="gray80"))

if (save_plots) ggsave(filename="line4b.png", width=6, height=4)

p1_lines +
  scale_y_continuous(limits=c(0,10),
                     breaks=seq(0,10,2.5),
                     labels=scales::label_percent(scale = 1),
                     expand = c(0, NA)) +
  theme(panel.grid.major.y = element_line(color="gray80"))

if (save_plots) ggsave(filename="line4c.png", width=6, height=4)



# reverse the grid lines
p1_lines +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line(color="gray80"),
        axis.ticks.y = element_line(),
        axis.ticks.x = element_blank(),
        axis.line.y.left = element_line(linewidth=.25))

if (save_plots) ggsave(filename="line5.png", width=6, height=4)
```


### Limits and Aspect Ratio

```{r, fig.width=6, fig.height=4}
p1_limits <- congregations %>%
  ggplot(aes(x=year, y=percent)) +
  geom_line(linewidth=0.75) +
  scale_y_continuous(limits=c(0, 10),
                     breaks=seq(0,10,2),
                     labels=scales::label_percent(scale = 1),
                     expand = c(0, NA)) +
  labs(y="Congregations Advertising",
       x=NULL) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line.y.left = element_line(linewidth=.4),
        axis.line.x.bottom = element_line(linewidth=.4))

p1_limits
if (save_plots) ggsave(filename="line6a.png", width=6, height=4)
```

```{r, fig.width=6, fig.height=3.5}
p1_limits + 
  scale_y_continuous(limits=c(0, 8),
                     breaks=seq(0,10,2),
                     labels=scales::label_percent(scale = 1),
                     expand = c(0, NA))
  
if (save_plots) ggsave(filename="line6b.png", width=6, height=3.5)

if (save_plots) ggsave(filename="line6c.png", width=6, height=3)
  
if (save_plots) ggsave(filename="line6d.png", width=6, height=2.5)
  
if (save_plots) ggsave(filename="line6e.png", width=6, height=5)
```



### Relative Font Size

```{r, fig.width=6*.6, fig.height=3.5*.6}
congregations %>%
  ggplot(aes(x=year, y=percent)) +
  geom_line(linewidth=0.75) +
  scale_y_continuous(limits=c(0, 8),
                     breaks=seq(0,10,2),
                     labels=scales::label_percent(scale = 1),
                     expand = c(0, NA)) +
  labs(y="Congregations Advertising",
       x=NULL) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line.y.left = element_line(linewidth=.4),
        axis.line.x.bottom = element_line(linewidth=.4))

if (save_plots) ggsave(filename="line7a.png", width=6*.8, height=3.5*.8)
if (save_plots) ggsave(filename="line7b.png", width=6*.6, height=3.5*.6)
```

### Aggregate

```{r, fig.width=6*.7, fig.height=3.5*.7}
congregations %>%
  ggplot(aes(x=year, y=percent)) +
  geom_line(linewidth=0.75) +
  scale_y_continuous(limits=c(0, 8),
                     breaks=seq(0,10,2),
                     labels=scales::label_percent(scale = 1),
                     expand = c(0, NA)) +
  labs(y="Congregations Advertising",
       x=NULL) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line.y.left = element_line(linewidth=.4),
        axis.line.x.bottom = element_line(linewidth=.4),
        axis.title.y = element_text(size=10, color="gray40",
                                    margin=margin(r=10, unit="pt")),
        axis.text = element_text(size=10, color="gray40"))

if (save_plots) ggsave(filename="line8.png", width=6*.7, height=3.5*.7)
```


### Line Variations

```{r, fig.width=6*.7, fig.height=3.5*.7}
congregations %>%
  ggplot(aes(x=year, y=percent)) +
  geom_line(linewidth=0.5) +
  geom_point(size=.75) +
  scale_y_continuous(limits=c(0, 8),
                     breaks=seq(0,10,2),
                     labels=scales::label_percent(scale = 1),
                     expand = c(0, NA)) +
  labs(y="Congregations Advertising",
       x=NULL) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line.y.left = element_line(linewidth=.4),
        axis.line.x.bottom = element_line(linewidth=.4),
        axis.title.y = element_text(size=10, color="gray40",
                                    margin=margin(r=10, unit="pt")),
        axis.text = element_text(size=10, color="gray40"))

if (save_plots) ggsave(filename="line9a.png", width=6*.7, height=3.5*.7)
```

```{r, fig.width=6*.7, fig.height=3.5*.7}
congregations %>%
  ggplot(aes(x=year, y=percent)) +
  geom_area(linewidth=0.75, fill="gray60") +
  scale_y_continuous(limits=c(0, 8),
                     breaks=seq(0,10,2),
                     labels=scales::label_percent(scale = 1),
                     expand = c(0, NA)) +
  labs(y="Congregations Advertising",
       x=NULL) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line.y.left = element_line(linewidth=.4),
        axis.line.x.bottom = element_line(linewidth=.4),
        axis.title.y = element_text(size=10, color="gray40",
                                    margin=margin(r=10, unit="pt")),
        axis.text = element_text(size=10, color="gray40"))

if (save_plots) ggsave(filename="line9b.png", width=6*.7, height=3.5*.7)
```

```{r, fig.width=6*.7, fig.height=3.5*.7}
congregations %>%
  ggplot(aes(x=year, y=percent)) +
  geom_smooth(linewidth=0.75, color="gray70", se=FALSE) +
  geom_point(size=1) +
  scale_y_continuous(limits=c(0, 8),
                     breaks=seq(0,10,2),
                     labels=scales::label_percent(scale = 1),
                     expand = c(0, NA)) +
  labs(y="Congregations Advertising",
       x=NULL) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line.y.left = element_line(linewidth=.4),
        axis.line.x.bottom = element_line(linewidth=.4),
        axis.title.y = element_text(size=10, color="gray40",
                                    margin=margin(r=10, unit="pt")),
        axis.text = element_text(size=10, color="gray40"))

if (save_plots) ggsave(filename="line9c.png", width=6*.7, height=3.5*.7)
```

```{r, fig.width=6*.7, fig.height=3.5*.7}
congregations %>%
  ggplot(aes(x=year, y=percent)) +
  geom_bar(fill="gray60", width=1, stat="identity", color="gray60") +
  scale_y_continuous(limits=c(0, 8),
                     breaks=seq(0,10,2),
                     labels=scales::label_percent(scale = 1),
                     expand = c(0, NA)) +
  labs(y="Congregations Advertising",
       x=NULL) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line.y.left = element_line(linewidth=.4),
        axis.line.x.bottom = element_line(linewidth=.4),
        axis.title.y = element_text(size=10, color="gray40",
                                    margin=margin(r=10, unit="pt")),
        axis.text = element_text(size=10, color="gray40"))

if (save_plots) ggsave(filename="line9d.png", width=6*.7, height=3.5*.7)
```




# Mean Comparison

```{r}
embryos <- read_excel("allele_data.xlsx")
```


## Original

An approximation to the original visualization  Data are approximated from:

Duddy, G., Courtis, K., Horwood, J. et al. Donor template delivery by recombinant adeno-associated virus for the production of knock-in mice. BMC Biol 22, 26 (2024). https://doi.org/10.1186/s12915-024-01834-z

Figure 3a

```{r, fig.width=2.25, fig.height=3}
embryos %>%
  mutate(titre = factor(titre)) %>%
  ggplot(aes(x=titre, y=percent, shape=titre)) +
  geom_bar(stat="summary", fun=mean, color="gray10", fill=c("gray40", "gray70"),
           width=.6) +
  geom_errorbar(stat="summary", fun.data = mean_sd, width=.2) +
  geom_quasirandom(size=2, width=.2, varwidth = TRUE) + 
  stat_compare_means(comparisons=list(c(1, 2)), 
                     label.y=90, method="t.test", label="p.signif",
                     symnum.args = list(cutpoints = c(0, 0.05, Inf), 
                                        symbols = c("****", "P>0.05"))) +
  scale_y_continuous(limits=c(0,100),
                     breaks=seq(0,100,20),
                     expand=c(0,NA),
                     name="% Targeted") +
  scale_x_discrete(labels=c(bquote(1~"x"~10^9), bquote(1~"x"~10^10)),
                   name="VGC/ml") +
  scale_shape_manual(values=c(19, 15)) +
  theme_minimal() + 
  theme(legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(),
        axis.ticks = element_line(),
        text = element_text(size=12, color="gray10", face="bold"),
        axis.text = element_text(size=12, color="gray10"))

if (save_plots) ggsave("means1.png", width=2.25, height=3)
```


## Revision Options

### Remove Bars, Add Means

```{r, fig.width=2.25, fig.height=3}
embryos %>%
  mutate(titre = factor(titre)) %>%
  ggplot(aes(x=titre, y=percent, shape=titre)) +
  geom_quasirandom(size=1.5, width=.2, varwidth = TRUE, color="gray") + 
  geom_boxplot(color="black", width=.3, fill=NA) +
  stat_compare_means(comparisons=list(c(1, 2)), 
                     label.y=90, method="t.test", label="p.signif",
                     symnum.args = list(cutpoints = c(0, 0.05, Inf), 
                                        symbols = c("****", "P>0.05"))) +
  scale_y_continuous(limits=c(0,100),
                     breaks=seq(0,100,20),
                     expand=c(0,NA),
                     name="% Targeted") +
  scale_x_discrete(labels=c(bquote(1~"x"~10^9), bquote(1~"x"~10^10)),
                   name="VGC/ml") +
  scale_shape_manual(values=c(19, 15)) +
  theme_minimal() + 
  theme(legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(),
        axis.ticks = element_line(),
        text = element_text(size=12, color="gray10", face="bold"),
        axis.text = element_text(size=12, color="gray10"))

if (save_plots) ggsave("means2.png", width=2.25, height=3)
```


```{r, fig.width=2.25, fig.height=3}
means <- embryos %>%
  mutate(titre = factor(titre)) %>%
  group_by(titre) %>%
  summarize(mean_se(percent, mult=1.96))
embryos %>%
  mutate(titre = factor(titre)) %>%
  ggplot(aes(x=titre, y=percent)) +
  geom_quasirandom(size=1.5, width=.2, varwidth = TRUE, color="gray60") + 
  geom_pointrange(data=means, aes(x=titre, y=y, ymin=ymin, ymax=ymax), 
                  size=1, linewidth=.75, shape=15, color="red") +
  stat_compare_means(comparisons=list(c(1, 2)), 
                     label.y=90, method="t.test", label="p.signif",
                     symnum.args = list(cutpoints = c(0, 0.05, Inf), 
                                        symbols = c("****", "P>0.05"))) +
  scale_y_continuous(limits=c(0,100),
                     breaks=seq(0,100,20),
                     expand=c(0,NA),
                     name="% Targeted") +
  scale_x_discrete(labels=c(bquote(1~"x"~10^9), bquote(1~"x"~10^10)),
                   name="VGC/ml") +
  theme_minimal() + 
  theme(legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(),
        axis.ticks = element_line(),
        text = element_text(size=12, color="gray10", face="bold"),
        axis.text = element_text(size=12, color="gray10"))

if (save_plots) ggsave("means3.png", width=2.25, height=3)
```


### Make the points visible

```{r, fig.width=2.25, fig.height=3}
means <- embryos %>%
  mutate(titre = factor(titre)) %>%
  group_by(titre) %>%
  summarize(mean_se(percent, mult=1.96))
embryos %>%
  mutate(titre = factor(titre)) %>%
  ggplot(aes(x=titre, y=percent)) +
  geom_quasirandom(size=1.5, width=.2, varwidth = TRUE, color="gray60") + 
  geom_pointrange(data=means, aes(x=titre, y=y, ymin=ymin, ymax=ymax), 
                  size=1, linewidth=.75, shape=15, color="red") +
  stat_compare_means(comparisons=list(c(1, 2)), 
                     label.y=90, method="t.test", label="p.signif",
                     symnum.args = list(cutpoints = c(0, 0.05, Inf), 
                                        symbols = c("****", "P>0.05"))) +
  scale_y_continuous(limits=c(0,100),
                     breaks=seq(0,100,20),
                     expand=expansion(add=c(3,0)),
                     name="% Targeted") +
  scale_x_discrete(labels=c(bquote(1~"x"~10^9), bquote(1~"x"~10^10)),
                   name="VGC/ml") +
  theme_minimal() + 
  theme(legend.position = "none",
        panel.grid = element_blank(),
        axis.line.y = element_line(),
        axis.ticks.y = element_line(),
        text = element_text(size=12, color="gray10", face="bold"),
        axis.text = element_text(size=12, color="gray10"))

if (save_plots) ggsave("means4.png", width=2.25, height=3)
```



### Labels

```{r, fig.width=2.25, fig.height=3}
means <- embryos %>%
  mutate(titre = factor(titre)) %>%
  group_by(titre) %>%
  summarize(mean_se(percent, mult=1.96))
embryos %>%
  mutate(titre = factor(titre)) %>%
  ggplot(aes(x=titre, y=percent)) +
  geom_beeswarm(cex=3, color="gray60", side=-1) + 
  geom_pointrange(data=means, aes(x=c(1.17, 2.17), y=y, ymin=ymin, ymax=ymax), 
                  size=.75, linewidth=.75, shape=15, color="red") +
    stat_compare_means(comparisons=list(c(1, 2)), 
                       label.y=85, method="t.test", label="p.signif",
                       size=3, 
                     symnum.args = list(cutpoints = c(0, 0.05, Inf), 
                                        symbols = c("****", "Mean Difference\np-value > 0.05"))) +
  scale_y_continuous(limits=c(0,100),
                     breaks=seq(0,100,20),
                     expand=expansion(add=c(3,0)),
                     labels=scales::label_percent(scale=1),
                     name="Per Embryo Knock-in Efficiency") +
  scale_x_discrete(labels=c(bquote(1~"x"~10^9), bquote(1~"x"~10^10)),
                   name="VGC/ml") +
  coord_cartesian(clip="off") +
  theme_minimal() + 
  theme(legend.position = "none",
        panel.grid = element_blank(),
        axis.line.y = element_line(linewidth=.3),
        axis.ticks.y = element_line(),
        text = element_text(size=10, color="gray10"),
        axis.text = element_text(size=10, color="gray10"))

if (save_plots) ggsave("means5.png", width=2.25, height=3)
```


### Flip It

```{r, fig.width=4*1.25, fig.height=1.75*1.25}
means <- embryos %>%
  mutate(titre = factor(titre)) %>%
  group_by(titre) %>%
  summarize(mean_se(percent, mult=1.96))
embryos %>%
  mutate(titre = fct_rev(factor(titre))) %>%
  ggplot(aes(x=titre, y=percent)) +
  geom_beeswarm(cex=4, color="gray60", side=0) + 
  geom_pointrange(data=means, aes(x=c(1.75, .75), 
                                  y=y, ymin=ymin, ymax=ymax), 
                  size=.75, linewidth=.75, shape=15, color="red") +
    stat_compare_means(comparisons=list(c(1, 2)), label.y=85,
                       method="t.test", label="p.signif",
                       size=3, angle=0, hide.ns = TRUE) +
  annotate("text", x=1.5, y=92, label="Mean difference\np-value > 0.05",
           size=3, hjust=0) +
  scale_y_continuous(limits=c(0,100),
                     breaks=seq(0,100,20),
                     expand=c(0,NA),
                     labels=scales::label_percent(scale=1),
                     name="Per Embryo Knock-in Efficiency") +
  scale_x_discrete(labels=c(bquote(1~"x"~10^10), bquote(1~"x"~10^9)),
                   name="VGC/ml") +
  coord_flip(clip="off") +
  theme_minimal() + 
  theme(legend.position = "none",
        plot.margin = margin(l=.5,r=2,b=.2, unit="cm"),
        panel.grid = element_blank(),
        axis.line.x = element_line(linewidth=.3),
        axis.ticks.x = element_line(),
        text = element_text(size=10, color="gray10"),
        axis.text = element_text(size=10, color="gray10"),
        axis.text.y = element_text(hjust=0, margin=margin(r=8, unit="pt")),
        axis.title.x = element_text(vjust=0))

if (save_plots) ggsave("means6.png", width=4*1.25, height=1.75*1.25)
```




# Increase/decrease

An approximation to the original visualization  Data are approximated from:

Duddy, G., Courtis, K., Horwood, J. et al. Donor template delivery by recombinant adeno-associated virus for the production of knock-in mice. BMC Biol 22, 26 (2024). https://doi.org/10.1186/s12915-024-01834-z

Figure 3b

```{r}
alleles <- read_excel("allele_data.xlsx", sheet=2)
```


## Original

```{r, fig.width=4, fig.height=3.5}
alleles_wide <- pivot_wider(alleles, names_from=titre, values_from=percent,
                            names_prefix="c")
alleles %>%
  mutate(titre = factor(titre),
         allele = factor(allele, levels=c("GMAF", "GMAG", "GMAJ", "GMAN", 
                                          "GMAW", "GMAZ", "IRCG", "GMAL", "RLEB"))) %>%
  ggplot(aes(x=titre, y=percent, color=allele)) +
  geom_point() +
  geom_segment(data = alleles_wide, mapping=aes(x=1, xend=2, y=c9, yend=c10, color=allele)) +
  scale_x_discrete(labels=c(bquote(1~"x"~10^9), bquote(1~"x"~10^10)),
                   name="VGC/ml") +
  scale_y_continuous(limits = c(0,50), expand=c(0, NA),
                     name="% Targeted") +
  scale_color_manual(name=NULL, values=c("blue", "red", "green", "black",
                                        "darkblue", "purple", "darkred", "gold", "lightblue")) +
  coord_cartesian(clip="off") +
  guides(color=guide_legend(ncol=2)) +
  theme_minimal() +
  theme(legend.position = "inside",
        legend.position.inside = c(.25, .9),
        panel.grid = element_blank(),
        plot.margin = margin(t=.5, unit="in"),
        axis.line = element_line(),
        axis.ticks.y = element_line(),
        text = element_text(size=12, color="gray10"),
        axis.text = element_text(size=12, color="gray10", face="bold"),
        axis.title = element_text(size=12, color="gray10", face="bold"),
        legend.key.height = unit(12, "pt"),
        legend.text = element_text(size=9, face="bold"))

if (save_plots) ggsave("slope1.png", width=4, height=3.5)
```


## Revision Options

### Step 1

```{r, fig.width=3, fig.height=3.5}
alleles_wide <- pivot_wider(alleles, names_from=titre, values_from=percent,
                            names_prefix="c")
alleles %>%
  mutate(titre = factor(titre),
         allele = factor(allele, levels=c("GMAF", "GMAG", "GMAJ", "GMAN", 
                                          "GMAW", "GMAZ", "IRCG", "GMAL", "RLEB"))) %>%
  ggplot(aes(x=titre, y=percent, color=allele)) +
  geom_point() +
  geom_segment(data = alleles_wide, 
               mapping=aes(x=1, xend=2, y=c9, yend=c10, color=allele)) +
  geom_text(data = alleles_wide, aes(label=allele, x=2.2, y=c10),
            position = position_nudge(y = c(-1,0,0,0,0,1,0,0,-2)),
            size=3.5) +
  scale_x_discrete(labels=c(bquote(1~"x"~10^9), bquote(1~"x"~10^10)),
                   name="VGC/ml", expand=expansion(add=.2)) +
  scale_y_continuous(limits = c(0,50), expand=c(0, NA),
                     name="Per Allele Knock-in Efficiency",
                     labels=scales::label_percent(scale=1)) +
  scale_color_manual(name=NULL, values=c("blue", "red", "green", "black",
                                        "darkblue", "purple", "darkred", "gold", "lightblue")) +
  coord_cartesian(clip="off") +
  theme_minimal() +
  theme(legend.position="none",
        panel.grid = element_blank(),
        plot.margin = margin(t=.1, r=.5, unit="in"),
        axis.line.y = element_line(),
        axis.ticks.y = element_line(),
        axis.text.x = element_text(margin=margin(t=10, unit="pt")),
        text = element_text(size=12, color="gray10"),
        axis.text = element_text(size=12, color="gray10", face="bold"),
        axis.title = element_text(size=12, color="gray10", face="bold"))

if (save_plots) ggsave("slope2.png", width=3, height=3.5)
```


### Color

```{r, fig.width=3, fig.height=3.5}
alleles_wide <- pivot_wider(alleles, names_from=titre, values_from=percent,
                            names_prefix="c") %>%
  mutate(increase = c10 > c9)
alleles <- alleles %>%
  mutate(titre = factor(titre)) %>%
  left_join(select(alleles_wide, allele, increase), by="allele")

alleles_wide %>%
  ggplot(aes(color=increase)) +
  geom_point(data = alleles, aes(x=titre, y=percent)) +
  geom_segment(data = alleles_wide, mapping=aes(x=1, xend=2, y=c9, yend=c10, color=increase)) +
  geom_text(data = alleles_wide, aes(label=allele, x=2.25, y=c10),
            position = position_nudge(y = c(-1,0,0,0,0,1,0,0,-2)),
            size=3.7) +
  scale_x_discrete(labels=c(bquote(1~"x"~10^9), bquote(1~"x"~10^10)),
                   name="VGC/ml", expand=expansion(add=.2)) +
  scale_y_continuous(limits = c(0,50), expand=c(0, NA),
                     name="Per Allele Knock-in Efficiency",
                     labels=scales::label_percent(scale=1)) +
  scale_color_manual(name=NULL, values=c("gray70", "darkred")) +
  coord_cartesian(clip="off") +
  theme_minimal() +
  theme(legend.position="none",
        panel.grid = element_blank(),
        plot.margin = margin(t=.1, r=.5, l=.2, unit="in"),
        axis.line.y = element_line(),
        axis.ticks.y = element_line(),
        axis.text.x = element_text(margin=margin(t=10, unit="pt")),
        text = element_text(size=12, color="gray10"),
        axis.text = element_text(size=12, color="gray10"),
        axis.title = element_text(size=12, color="gray10"),
        axis.title.y = element_text(margin=margin(r=10, unit="pt")))

if (save_plots) ggsave("slope3.png", width=3, height=3.5)
```



# Bar Chart

The salary data was computed from data shared along with the publication 
"Who Gets Hired? Political Patronage and Bureaucratic Favoritism," Mai Hassan, Horacio Larreguy, Stuart Russell.  American Political Science Review, 25 January 2024, https://doi.org/10.1017/S0003055423001338.  

The data and code are published at 
Hassan, Mai; Larreguy, Horacio; Russell, Stuart, 2024, "Replication Data for: Who Gets Hired? Political Patronage and Bureaucratic Favoritism", https://doi.org/10.7910/DVN/MLZ39X, Harvard Dataverse, V1, UNF:6:B4LCOg2sJocG8bwJeR2WdQ== [fileUNF] 


```{r}
salary <- read_csv("salary_counts.csv")
```



### Original Plot

The original plot was created in Stata.  This code approximates the original published image.

```{r, fig.width=6, fig.height=6/1.6}
ggplot(salary, 
       aes(x=salary_group, y=count)) +
  geom_col(width=.8, fill = "gray40") +
  scale_x_continuous(limits=c(.5,21),
                     breaks=1:20,
                     labels=ifelse(1:20 %% 2 == 1, 1:20, ""),
                     expand=c(0,NA)) +
  scale_y_continuous(limits=c(0,35000),
                     breaks=seq(0,35000, 5000),
                     labels=ifelse(seq(0,35000, 5000) %% 10000 == 0, seq(0,35000, 5000), "")) +
  geom_vline(xintercept=9.5, color="red", linetype="dotted") +
  annotate("text",
           x=c(2, 13),
           y=c(35000, 35000),
           label=c("1-9 managed by Nairobi", "10-20 managed by localities"),
           size=2.8, hjust=0) +
  labs(y="Frequency",
       x="Salary group") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.y = element_text(angle=90, hjust=.5),
        axis.text = element_text(color="black", size=10),
        axis.title = element_text(color="black", size=10),
        line = element_line(color="black"))

if (save_plots) ggsave("bar1a.png", width=6, height=6/1.6)
```

Here's an equivalent default bar plot in R

```{r, fig.width=6, fig.height=6/1.6}
ggplot(salary, 
       aes(x=salary_group, y=count)) +
  geom_col(width=.9) +
  geom_vline(xintercept=9.5, color="red", linetype="dotted") +
  annotate("text",
           x=c(2, 13),
           y=c(35000, 35000),
           label=c("1-9 managed by Nairobi", "10-20 managed by localities"),
           size=2.8, hjust=0) +
  labs(y="Frequency",
       x="Salary group") +
  theme_bw() +
  theme(panel.grid = element_blank())

```


## Revisions


### Lines, Colors, Improved Annotations

```{r, fig.width=6, fig.height=6/1.6}
ggplot(salary, 
       aes(x=salary_group, y=count)) +
  geom_col(width=.8, fill=c(rep("gray30", 8), rep("gray70", 11))) +
  scale_x_continuous(breaks = 2:20,
                     expand=c(0,NA)) +
  scale_y_continuous(expand=c(0,NA),
                     labels = scales::label_comma()) +
  geom_vline(xintercept=9.5, color="red", linetype="dotted") +
  annotate("text",
           x=c(5, 12.5),
           y=c(25000, 25000),
           label=c("High salary groups\nmanaged by Nairobi", 
                   "Low salary groups\nmanaged by localities"),
           size=3, hjust=0.5) +
  labs(y="Number of Bureaucrats",
       x="Salary Group") +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.text = element_text(size=10, color="gray10"),
        axis.title = element_text(size=10, color="gray10"))

if (save_plots) ggsave("bar2.png", width=6, height=6/1.6)
```


### Alternate Annotation

```{r, fig.width=6, fig.height=6/1.6}
ggplot(salary, 
       aes(x=salary_group, y=count)) +
  geom_col(width=.8, fill=c(rep("gray30", 8), rep("gray70", 11))) +
  scale_x_continuous(breaks = 2:20) +
  scale_y_continuous(expand=c(0,NA),
                     breaks=c(0,10000,20000,30000),
                     labels = scales::label_comma()) +
  coord_cartesian(clip="off") +
  annotate("text",
           x=c(5.5, 15.5),
           y=c(33000, 33000),
           label=c("High salary groups\nmanaged by Nairobi", 
                   "Low salary groups\nmanaged by localities"),
           size=3, hjust=0.5, vjust=0) +
  annotate("segment",
           x=c(1.7, 9.7), xend=c(9.3, 20.3),
           y=c(32500,32500), yend=c(32500,32500),
           linewidth=.25) +
  labs(y="Number of Bureaucrats",
       x="Salary Group") +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        axis.line.y = element_line(linewidth=.25),
        axis.ticks.y = element_line(linewidth=.25),
        axis.text = element_text(size=10, color="gray10"),
        axis.title = element_text(size=10, color="gray10"),
        plot.margin = margin(t=1, unit="cm"))

if (save_plots) ggsave("bar3.png", width=6, height=6/1.6)
```



### Revision 3

```{r, fig.width=2.5, fig.height=4.5}
ggplot(salary, 
       aes(x=salary_group, y=count)) +
  geom_col(width=.8, fill=c(rep("gray30", 8), rep("gray70", 11))) +
  scale_x_reverse(breaks = 2:20,
                     expand=c(0,NA)) +
  scale_y_continuous(expand=c(0,NA), breaks=c(0,15000,30000),
                     labels = scales::label_comma()) +
  annotate("text",
           x=c(5, 11.5),
           y=c(19000,19000),
           color=c("gray30", "gray60"),
           label=c("High salary groups\nmanaged by Nairobi\n(5% of positions)", 
                   "Low salary groups\nmanaged by localities\n(95% of positions)"),
           size=3, hjust=0.5) +
  coord_flip(clip="off") +
  labs(y="Number of Bureaucrats",
       x="Salary Group") +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        plot.margin = margin(r=.1, unit="in"),
        axis.ticks.x = element_line(linewidth=.25),
        axis.text = element_text(size=10, color="gray10"),
        axis.title = element_text(size=10, color="gray10"),
        axis.title.x = element_text(margin=margin(t=10, unit="pt")))

if (save_plots) ggsave("bar4.png", width=2.5, height=4.5)
```


# Brainstorm

Data for the brainstorm exercise, in a few different formats:

```{r}
zoo_long_table <- tribble(~animal, ~year, ~count,
                          "Bears", 2022, 4,
                          "Bears", 2023, 6,
                          "Turtles", 2022, 10,
                          "Turtles", 2023, 8,
                          "Parrots", 2022, 3,
                          "Parrots", 2023, 7)

zoo_table_year_columns <- pivot_wider(zoo_long_table,
                                      names_from=year,
                                      values_from=count)

zoo_table_animal_columns <- pivot_wider(zoo_long_table, 
                                        names_from=animal, 
                                        values_from=count)

zoo_long_individual <- data.frame(animal=c(rep("Bears", 10),
                                           rep("Turtles", 18),
                                           rep("Parrots", 10)),
                                  year=c(rep(2022, 4), rep(2023, 6),
                                         rep(2022, 10), rep(2023, 8),
                                         rep(2022, 3), rep(2023, 7)))
```






